---
title: "BBets Project"
author: "Jose Torres Vargas"
date: "03/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1. what is his expected win/loss amount,  
2. how much would the instructor have to wager to make the bet fair 
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365

nStudents = 28
nBets = nStudents * 15
saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:nBets){
    sampleClass = sample(days,nStudents, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == nStudents) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```

Answer questions #1



```{r}
print('average amt:')
print(mean(saveArray))
```

# Answers
What is his expected win/loss amount? 

35 students 2:1 
It's expected to win $232.779

How much would the instructor have to wager to make the bet fair?

In order for it to be fair, you will have to change the winnings to 4.3 to 4.4 from my trials an average of 7.44.

How many students would have to be in the class for a 2:1 bet to be fair?

The closest number of students would have to be 28, with an average of -15.39.
  